Comparing Predictor Types One Annotation At A Time

### 2019-04-16 Scripts/comparing_predictortypes_one_annot_at_a_time.Rmd
editted script

@@

>>>>

write.csv(t(rfimpvarsmat_gm12878_10kb)[,c(1,3,2)], "C:/Users/stili/Documents/TAD_miscellaneous/tables/rfimpvarsmat_gm12878_10kb.csv")

@@

##25kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/training_testing/train.rds")
train <- train[,-grep("_binary", names(train))]

rfimpvarsmat_gm12878_25kb <- matrix(nrow=3, ncol=107,
				dimnames=list("Predictor Type"=c("OC",
												 "Distance",
												 "OP"),
							  "Annotation"=unique(gsub(paste0(c("Gm12878", 
																"_count", 
																"_perc", 
																"_dist",
																"-",
																"Haib", 
																"Sydh",
																"Uta",
																"Uw",
																"Broad",
																"Uchicago"), collapse = "|"), "", names(train_smote)[-1]))))

	rfimpvarsmat_gm12878_25kb[,i+1] <- varImp(rfModel)$importance[,1][order(rownames(varImp(rfModel)$importance))]
}

write.csv(t(rfimpvarsmat_gm12878_25kb)[,c(1,3,2)], "C:/Users/stili/Documents/TAD_miscellaneous/tables/rfimpvarsmat_gm12878_25kb.csv")
```

##50kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/training_testing/train.rds")
train <- train[,-grep("_binary", names(train))]

rfimpvarsmat_gm12878_50kb <- matrix(nrow=3, ncol=107,
				dimnames=list("Predictor Type"=c("OC",
												 "Distance",
												 "OP"),
							  "Annotation"=unique(gsub(paste0(c("Gm12878", 
																"_count", 
																"_perc", 
																"_dist",
																"-",
																"Haib", 
																"Sydh",
																"Uta",
																"Uw",
																"Broad",
																"Uchicago"), collapse = "|"), "", names(train_smote)[-1]))))

	rfimpvarsmat_gm12878_50kb[,i+1] <- varImp(rfModel)$importance[,1][order(rownames(varImp(rfModel)$importance))]
}

write.csv(t(rfimpvarsmat_gm12878_50kb)[,c(1,3,2)], "C:/Users/stili/Documents/TAD_miscellaneous/tables/rfimpvarsmat_gm12878_50kb.csv")
```

##100kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/training_testing/train.rds")
train <- train[,-grep("_binary", names(train))]

rfimpvarsmat_gm12878_100kb <- matrix(nrow=3, ncol=107,
				dimnames=list("Predictor Type"=c("OC",
												 "Distance",
												 "OP"),
							  "Annotation"=unique(gsub(paste0(c("Gm12878", 
																"_count", 
																"_perc", 
																"_dist",
																"-",
																"Haib", 
																"Sydh",
																"Uta",
																"Uw",
																"Broad",
																"Uchicago"), collapse = "|"), "", names(train_smote)[-1]))))

	rfimpvarsmat_gm12878_100kb[,i+1] <- varImp(rfModel)$importance[,1][order(rownames(varImp(rfModel)$importance))]
}

write.csv(t(rfimpvarsmat_gm12878_100kb)[,c(1,3,2)], "C:/Users/stili/Documents/TAD_miscellaneous/tables/rfimpvarsmat_gm12878_100kb.csv")
```

# K562

```{r}
train <- readRDS("Z:/TAD_data_analysis/K562/10kb/training_testing/train.rds")
train <- train[,-grep("_binary", names(train))]

rfimpvarsmat_K562_10kb <- matrix(nrow=3, ncol=141,
				dimnames=list("Predictor Type"=c("OC",
												 "Distance",
												 "OP"),
							  "Annotation"=unique(gsub(paste0(c("K562", 
																"_count", 
																"_perc", 
																"_dist",
																"-",
																"Haib", 
																"Sydh",
																"Uta",
																"Uw",
																"Broad",
																"Uchicago"), collapse = "|"), "", names(train_smote)[-1]))))

for(i in 0:140){
  print(names(train_smote)[(i*3+2):(i*3+4)])
	rfModel <- train(y~., data=train_smote[,c(1, (i*3+2):(i*3+4))], 
                 method="rf", 
                 metric="ROC", 
                 tuneGrid=tunegrid, 
                 trControl=fitControl, 
                 ntree=500) #as.numeric(rownames(results)[1]))

	rfimpvarsmat_K562_10kb[,i+1] <- varImp(rfModel)$importance[,1][order(rownames(varImp(rfModel)$importance))]
}

write.csv(t(rfimpvarsmat_K562_10kb)[,c(1,3,2)], "C:/Users/stili/Documents/TAD_miscellaneous/tables/rfimpvarsmat_K562_10kb.csv")

##25kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/K562/25kb/training_testing/train.rds")
train <- train[,-grep("_binary", names(train))]

rfimpvarsmat_K562_25kb <- matrix(nrow=3, ncol=141,
				dimnames=list("Predictor Type"=c("OC",
												 "Distance",
												 "OP"),
							  "Annotation"=unique(gsub(paste0(c("K562", 
																"_count", 
																"_perc", 
																"_dist",
																"-",
																"Haib", 
																"Sydh",
																"Uta",
																"Uw",
																"Broad",
																"Uchicago"), collapse = "|"), "", names(train_smote)[-1]))))

for(i in 0:140){
  print(names(train_smote)[(i*3+2):(i*3+4)])
	rfModel <- train(y~., data=train_smote[,c(1, (i*3+2):(i*3+4))], 
                 method="rf", 
                 metric="ROC", 
                 tuneGrid=tunegrid, 
                 trControl=fitControl, 
                 ntree=500) #as.numeric(rownames(results)[1]))

	rfimpvarsmat_K562_25kb[,i+1] <- varImp(rfModel)$importance[,1][order(rownames(varImp(rfModel)$importance))]
}

write.csv(t(rfimpvarsmat_K562_25kb)[,c(1,3,2)], "C:/Users/stili/Documents/TAD_miscellaneous/tables/rfimpvarsmat_K562_25kb.csv")
```

##50kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/K562/50kb/training_testing/train.rds")
train <- train[,-grep("_binary", names(train))]

rfimpvarsmat_K562_50kb <- matrix(nrow=3, ncol=141,
				dimnames=list("Predictor Type"=c("OC",
												 "Distance",
												 "OP"),
							  "Annotation"=unique(gsub(paste0(c("K562", 
																"_count", 
																"_perc", 
																"_dist",
																"-",
																"Haib", 
																"Sydh",
																"Uta",
																"Uw",
																"Broad",
																"Uchicago"), collapse = "|"), "", names(train_smote)[-1]))))

for(i in 0:140){
  print(names(train_smote)[(i*3+2):(i*3+4)])
	rfModel <- train(y~., data=train_smote[,c(1, (i*3+2):(i*3+4))], 
                 method="rf", 
                 metric="ROC", 
                 tuneGrid=tunegrid, 
                 trControl=fitControl, 
                 ntree=500) #as.numeric(rownames(results)[1]))

	rfimpvarsmat_K562_50kb[,i+1] <- varImp(rfModel)$importance[,1][order(rownames(varImp(rfModel)$importance))]
}

write.csv(t(rfimpvarsmat_K562_50kb)[,c(1,3,2)], "C:/Users/stili/Documents/TAD_miscellaneous/tables/rfimpvarsmat_K562_50kb.csv")
```

##100kb

```{r}
train <- readRDS("Z:/TAD_data_analysis/K562/100kb/training_testing/train.rds")
train <- train[,-grep("_binary", names(train))]

rfimpvarsmat_K562_100kb <- matrix(nrow=3, ncol=141,
				dimnames=list("Predictor Type"=c("OC",
												 "Distance",
												 "OP"),
							  "Annotation"=unique(gsub(paste0(c("K562", 
																"_count", 
																"_perc", 
																"_dist",
																"-",
																"Haib", 
																"Sydh",
																"Uta",
																"Uw",
																"Broad",
																"Uchicago"), collapse = "|"), "", names(train_smote)[-1]))))

for(i in 0:140){
  print(names(train_smote)[(i*3+2):(i*3+4)])
	rfModel <- train(y~., data=train_smote[,c(1, (i*3+2):(i*3+4))], 
                 method="rf", 
                 metric="ROC", 
                 tuneGrid=tunegrid, 
                 trControl=fitControl, 
                 ntree=500) #as.numeric(rownames(results)[1]))

	rfimpvarsmat_K562_100kb[,i+1] <- varImp(rfModel)$importance[,1][order(rownames(varImp(rfModel)$importance))]
}

write.csv(t(rfimpvarsmat_K562_100kb)[,c(1,3,2)], "C:/Users/stili/Documents/TAD_miscellaneous/tables/rfimpvarsmat_K562_100kb.csv")
```
